Data Processing Strategies to Determine Maximum Oxygen Uptake: A Systematic Scoping Review and Experimental Comparison with Guidelines for Reporting

### 2022-11-17 paper.qmd
Adjust to feedback by RR

**Methods** Out of a random sample, we investigated 242 recently published articles which measured V̇O~2max~ in an appropriate setting(Was ist das?). Reported data processing methods and their rationale were extracted. We compared the most common processing strategies on a data set of 72 standardized exercise tests in trained athletes.

**Results** Most studies use binned time averages to determine V̇O~2max~, with a minority using moving time or moving breath averages. Half of the included studies did not report their data processing strategy and almost all articles failed to provide a rationale for the particular strategy chosen. The processing strategies found in the literature can lead to median differences in V̇O~2max~ of more than 5% [RANGE_min, RANGE_max] with considerable variation at the individual level.

@@

-   Despite calls to use moving averages or digital filter, binned averages remain the most common data processing strategy to determine V̇O~2max~.
-   Different processing strategies lead to varying V̇O~2max~ values, which can hardly be predicted on an individual level (Verstehe ich nicht).
-   Researchers should at minimum report their processing strategy in detail, or preferably share their raw oxygen uptake data and analysis code.

@@

Researchers predominantly measure V̇O~2max~ during exercise tests to exhaustion. Among the factors that influence the V̇O~2max~ determination are the exercise test protocol [@buchfuhrer1983 ; @yoon2007; @midgley2008], exercise modality [@myers1991], motivation [@midgley2018], and biological variability [@katch1982]. The measuring method (e.g. mixing chamber, breath-by-breath) and the metabolic cart model used can influence the measured oxygen uptake --- and as such the V̇O~2max~ [@winkert2021; @miles1994]. (HIER EIN SATZ WARUM DIE DATEN ÜBERHAUPT PROZESSIERT WERDEN MÜSSEN). But even the same oxygen uptake data generated during an exercise test may result in varying outcomes when processed differently [@astorino2009].

@@

Measured gas exchange data is inherently noisy. Both the biological variability of breathing patterns and the measurement error (as well as irregular breaths such as coughs and swallowing) result in large fluctuation of raw oxygen uptake data on a breath-by-breath basis. To interpret the results the raw data therefore requires some form of processing to obtain a more stable estimate. However, different data processing strategies influence measured parameters of gas exchange [@matthews1987; @johnson1998; @astorino2009; @sell2021]. Midgley et al. @midgley2007 found differences in estimated VO~2max~ values between data processing strategies. As no difference regarding the reliability of the different approaches was found, no optimal strategy exists per se. Accordingly, when comparing outcomes within and across studies obviously a consistent processing strategy should be used. Based on own(???) data in sedentary and moderately trained individuals, Martin-Rincon et al. @martin-rincon2019 provided linear-log equations to compare mean V̇O~2max~ values derived from processing strategies with differing averaging interval lengths. The results showed ... . Furhtermore, there is inconclusive evidence on whether the influence of different processing strategies interacts with different exercise protocols [@hill2003; @scheadler2017].

Researchers have proposed a variety of calculation intervals and computational methods to process oxygen uptake data [@howley1995; @robergs2003; @ats/accp2003; @weir2004; @robergs2010] and calls to standardize processing strategies are frequent [@scheadler2017; @myers1990; @hill2003; @johnson1998]. In light of the influence on outcome variables, many articles highlighted the need to report processing strategies in research [@myers1990; @astorino2009; @scheadler2017; @johnson1998]. Midgley et al. @midgley2007 were the first to evaluate reported data processing strategies for breath-by-breath analyses in selected journals. They found that almost all studies reporting the use of binned time averaging, with only 1 in 117 using a moving time and a moving breath average, respectively. One third of the studies did not describe their processing method at all. While providing interesting first insights into reporting and processing practices, the search by Midgley et al. @midgley2007 was not systematic and its methods were not described in detail (DER SATZ IST GEFHÄHRLICH UND SOLLTE POSITIVER WAS DER ARTIKEL ÜBER DIE ERGEBNISSE VON MIDGLEY HINAUS NEUES BRINGT).

Robergs et al. @robergs2010 argued that to investigate the current state of data processing strategies, two possible approaches are *"(i) a summary of published research, and (ii) a survey circulated via the Internet to as many exercise physiologists as possible"*. They chose the latter approach with a total of 75 respondents, who reported a great variety in data processing strategies. Most researchers reported the use of binned time averages over 30 or 60 seconds. Surprinsingly, about half of the respondents admitted that their data processing strategy was rather chosen due to subjective factors as opposed to objective criteria [@robergs2010]. The present work therefore aims to investigate to what extent reporting and processing practices have followed the recommendations put forth by @midgley2007 and @robergs2003.

@@

Differences in estimated V̇O~2max~ vaules due to variation in data processing can have serious implications in practice. For example, the assessment of longitudinal data from athletes which  participated in diagnostics using differing data processing approaches becomes problematic or the pooling of results across studies in meta-analyses [@martin-rincon2019]. Data processing strategies directly affect the occurrence of a plateau in oxygen uptake, the primary criterion for V̇O~2max~ [@astorino2009]. Crucially, in situations where individuals are classified by their V̇O~2max~ --- for example when describing the training status of a study population [@pauw2013; @decroix2016] or evaluating patients for a heart transplantation [@mancini1991] --- differing processing strategies can lead to misclassifications [@johnson1998].

@@

A total of N = 72 exercise tests were analyzed for this study. Due to a miscalculation, the preregistration had incorrectly stated a number of 76 tests. The data were from previous research on the metabolic profile of endurance runners [@quittmann_unpubl_a; @quittmann_unpubl_b]. The tested individuals were experienced distance runners (15 female, 54 male; three of the males participated in both studies). The V̇O~2max~ tests were conducted in March to September 2019 [@quittmann_unpubl_a] and March to October 2021 [@quittmann_unpubl_b], respectively, while using identical exercise protocols and test equipment. Participants run on a treadmill (saturn 300/100, h/p/cosmos sports & medical 127 GmbH, Nussdorf-Traunstein, Germany) with 1% inclination for 8 minutes at a velocity of 2.8 m·s^-1^ as a warm-up. After preparing the gas exchange measures, they started a ramp protocol with an initial speed of 2.8 m·s^-1^ for two minutes and subsequently increased velocity by 0.15 m·s^-1^ every 30 seconds. The researchers provided verbal encouragement and terminated the exercise when the participants reached subjective exhaustion.

@@

Out of the authors that provided information and collected breath-by-breath measurements, most (79.5%) utilized binned averages to determine V̇O~2max~. Moving time averages, or breath-based averages were uncommon (see @fig-strategies). No study used digital filtering methods to determine V̇O~2max~. HIER FÄNDE ICH EINE TABELLE BESSER. ZIEMLICH VIEL PLATZ FÜR WENIG INFO.

```{r}
#| echo: false
#| fig-cap: "Strategies for processing breath-by-breath data in the reviewed literature (n = 88)."
#| label: fig-strategies
#| out-width: '90%'

knitr::include_graphics("./plots/strategies.png")
```

@@

The calculation intervals for time-based averages of mixing chamber and breath-by-breath devices ranged from 5 to 60 seconds (see @fig-duration). 30-second intervals were most common to define V̇O~2max~, while some authors also often employed shorter (10-20 s) and longer (60 s) periods. (HIER GLAUBE ICH AUCH LIEBER TABELLE)

```{r}
#| echo: false
#| fig-cap: "Total durations of the calculation interval of V̇O~2max~ in the reviewed studies."
#| label: fig-duration
#| out-width: '90%'

@@

```{r}
#| echo: false
#| fig-cap: "V̇O~2max~ varies by data processing strategy. Values are expressed relative to the V̇O~2max~ from a 30-second binned average — the most common strategy as determined by the review. Solid lines display the median, the shaded areas mark the interval between 10th and 90th percentile. Using moving average leads to systematically higher V̇O~2max~ values compared to binned time averages. Changing the averaging interval (in seconds or breaths) can lead to median changes in V̇O~2max~ as large as 5%."
#| fig-scap: "Comparison of different data processing strategies."
#| label: fig-comparison
#| out-width: '90%'

knitr::include_graphics("./plots/comparison.png")
```

(SOLLTE DIE BESCHRIFTUNG AUF DER X-ACHSE NICHT DAUER SEIN)

@@

Despite calls to use moving averages or digital filters [@robergs2003; @robergs2010], binned time averages remain the most common data processing strategy to determine V̇O~2max~ in the reviewed literature (see @fig-strategies). The present findings are generally in agreement with the findings of the non-systematic search by Midgley et al. @midgley2007 and the survey by Robergs et al. @robergs2010. It is somewhat surprising, that practices have not changed in recent years despite the publication of recommendations discouraging researchers from using binned averages [@robergs2010]. Using binned time averages leads to systematically lower V̇O~2max~ values as compared to moving averages (see @fig-comparison). The peak in oxygen uptake may be attained between two averaging intervals, resulting in an underestimation of V̇O~2max~. Binned time averages undermine the most important argument in favour of measuring breath-by-breath: the high temporal resolution of data. Despite these arguments speaking against the use of binned time averages, the present review demonstrates that they remain extremely common in the scientific literature.

@@

The different data processing strategies found in the literature directly bias the V̇O~2max~ determination (see @fig-comparison), and as such influence the classification of individuals, the evaluation of training success, and the assessment of V̇O~2max~ attainment. In accordance with previous findings [@johnson1998; @astorino2009; @sell2021] longer calculation intervals lead to lower V̇O~2max~ values (see @fig-comparison). The analyzed data shows median differences up to 5-7% between processing strategies, which is in accordance with previous research [@martin-rincon2019]. Some studies reported even higher mean differences of up to 20% [@myers1990], but only when including raw breath-by-breath data in the comparison. The evaluation of unprocessed raw data for its maximum is highly erroneous and as such is not performed in research (see @fig-duration); so there is no reason to compare it to other strategies. While previous research was often conducted in sedentary or recreationally trained individuals, we now present evidence, that a similar effect of data processing strategies on V̇O~2max~ exists in trained athletes.

(HIER WÄRE NOCH ZUSÄTZLICHE INFO WAS TYPISCHE UNTERSCHIEDE IN INTERVENTIONSSTUDIEN SIND UM DIE VARIATION ZWISCHEN DEN METHODEN BESSER EINSCHÄTZEN ZU KÖNNEN).

@@

The exact impact of data processing strategies on the V̇O~2max~ is highly individual. Most research did present only comparisons of mean values, with results in accordance with those found here [@martin-rincon2019]. At the individual level, data processing strategies may impact V̇O~2max~ values with varying magnitudes. For example, for 10% of the investigated athletes a binned time average of 5 seconds leads to a V̇O~2max~ \<3% higher than by a 30-second average, while for another 10% the V̇O~2max~ was \>6% higher (see @fig-comparison). Current values reported and equation derived compare strategies on a group level [@martin-rincon2019], which improves comparizon of group results for meta-analyses or group classifications. However, at the individual level these equations can only be applied with a large margin of error. Changes in the impact of different data processing strategies on V̇O~2max~ range from 1-2% in some individuals to more than 10% in others. Hence when evaluating V̇O~2max~ data from different tests in a single individual obtained by using different processing methods, there is no way to accurately compare these values even when the processing strategies are reported. While the comparison of V̇O~2max~ from different processing strategies require their reporting for an sufficient analysis on a group level, on the individual level the raw data from each test is required.

@@

> *"We measured breath-by-breath data during the ramp tests with a ZAN 600 USB device (nSpire Health, Inc., Longmont, CO, United States of America). The raw data was analyzed without any previous filtering by using a low-pass forward-backward Butterworth filter (each filter: 3rd order, 0.04 Hz cut-off) implemented in the spiro package for R version 0.1.0 [@nolte2022]. This strategy produces similar results as that recommended by Robergs et al. @robergs2010, but does not include a time lag."*

>>>>

**Methods** Out of a random sample, we investigated 242 recently published articles which measured V̇O~2max~ during ramp tests. Reported data processing methods and their rationale were extracted. We compared the most common processing strategies on a data set of 72 standardized exercise tests in trained athletes.

**Results** Most studies use binned time averages to determine V̇O~2max~, with a minority using moving time or moving breath averages. Half of the included studies did not report their data processing strategy and almost all articles failed to provide a rationale for the particular strategy chosen. The processing strategies found in the literature can lead to median differences in V̇O~2max~ of more than 5% (range 0-7%) with considerable variation at the individual level.

@@

-   Despite calls to use moving averages or digital filter, binned averages remain the most common data processing strategy to determine V̇O~2max~.
-   Different processing strategies lead to varying V̇O~2max~ values at the median as well as at the individual level.
-   Researchers should at minimum report their processing strategy in detail, or preferably share their raw oxygen uptake data and analysis code.

@@

Researchers predominantly measure V̇O~2max~ during exercise tests to exhaustion. Among the factors that influence the V̇O~2max~ determination are the exercise test protocol [@buchfuhrer1983 ; @yoon2007; @midgley2008], exercise modality [@myers1991], motivation [@midgley2018], and biological variability [@katch1982]. The measuring method (e.g. mixing chamber, breath-by-breath) and the metabolic cart model used can influence the measured oxygen uptake --- and as such the V̇O~2max~ [@winkert2021; @miles1994]. Due to its inherent variation, the collected raw data data can hardly be interpreted without processing. The same oxygen uptake data generated during an exercise test may result in varying outcomes when processed differently [@astorino2009].

@@

Measured gas exchange data is inherently noisy. Both the biological variability of breathing patterns and the measurement error (as well as irregular breaths such as coughs and swallowing) result in large fluctuation of raw oxygen uptake data on a breath-by-breath basis. To interpret the results the raw data therefore requires some form of processing to obtain a more stable estimate. However, different data processing strategies influence measured parameters of gas exchange [@matthews1987; @johnson1998; @astorino2009; @sell2021]. Midgley et al. @midgley2007 found differences in estimated VO~2max~ values between data processing strategies. As no difference regarding the reliability of the different approaches was found, no optimal strategy exists per se. Accordingly, when comparing outcomes within and across studies obviously a consistent processing strategy should be used. Based on data in sedentary and moderately trained individuals, Martin-Rincon et al. @martin-rincon2019 provided linear-log equations to compare mean V̇O~2max~ values derived from processing strategies with differing averaging interval lengths. The results showed that reliability of V̇O~2max~ was higher in trained individuals, but not influenced by the data processing. Furthermore, there is inconclusive evidence on whether the influence of different processing strategies interacts with different exercise protocols [@hill2003; @scheadler2017].

Researchers have proposed a variety of calculation intervals and computational methods to process oxygen uptake data [@howley1995; @robergs2003; @ats/accp2003; @weir2004; @robergs2010] and calls to standardize processing strategies are frequent [@scheadler2017; @myers1990; @hill2003; @johnson1998]. In light of the influence on outcome variables, many articles highlighted the need to report processing strategies in research [@myers1990; @astorino2009; @scheadler2017; @johnson1998]. Midgley et al. @midgley2007 were the first to evaluate reported data processing strategies for breath-by-breath analyses in selected journals. They found that almost all studies reporting the use of binned time averaging, with only 1 in 117 using a moving time and a moving breath average, respectively. One third of the studies did not describe their processing method at all. In our article we will provide a systematic analysis of the reporting and usage of data processing strategies in recent literature.

Robergs et al. @robergs2010 argued that to investigate the current state of data processing strategies, two possible approaches are *"(i) a summary of published research, and (ii) a survey circulated via the Internet to as many exercise physiologists as possible"*. They chose the latter approach with a total of 75 respondents, who reported a great variety in data processing strategies. Most researchers reported the use of binned time averages over 30 or 60 seconds. Surprisingly, about half of the respondents admitted that their data processing strategy was rather chosen due to subjective factors as opposed to objective criteria [@robergs2010]. The present work therefore aims to investigate to what extent reporting and processing practices have followed the recommendations put forth by @midgley2007 and @robergs2003.

@@

Differences in estimated V̇O~2max~ values due to variation in data processing can have serious implications in practice. For example, the assessment of longitudinal data from athletes which participated in diagnostics using differing data processing approaches becomes problematic or the pooling of results across studies in meta-analyses [@martin-rincon2019]. Data processing strategies directly affect the occurrence of a plateau in oxygen uptake, the primary criterion for V̇O~2max~ [@astorino2009]. Crucially, in situations where individuals are classified by their V̇O~2max~ --- for example when describing the training status of a study population [@pauw2013; @decroix2016] or evaluating patients for a heart transplantation [@mancini1991] --- differing processing strategies can lead to misclassifications [@johnson1998].

@@

A total of N = 72 exercise tests were analyzed for this study. Due to a miscalculation, the preregistration had incorrectly stated a number of 76 tests. The data were from previous research on the metabolic profile of endurance runners [@quittmann_accepted; @schwarz2022]. The tested individuals were experienced distance runners (15 female, 54 male; three of the males participated in both studies). The V̇O~2max~ tests were conducted in March to September 2019 [@quittmann_accepted] and March to October 2021 [@schwarz2022], respectively, while using identical exercise protocols and test equipment. Participants run on a treadmill (saturn 300/100, h/p/cosmos sports & medical 127 GmbH, Nussdorf-Traunstein, Germany) with 1% inclination for 8 minutes at a velocity of 2.8 m·s^-1^ as a warm-up. After preparing the gas exchange measures, they started a ramp protocol with an initial speed of 2.8 m·s^-1^ for two minutes and subsequently increased velocity by 0.15 m·s^-1^ every 30 seconds. The researchers provided verbal encouragement and terminated the exercise when the participants reached subjective exhaustion.

@@

Out of the authors that provided information and collected breath-by-breath measurements, most (79.5%) utilized binned averages to determine V̇O~2max~. Moving time averages, or breath-based averages were uncommon (see @tbl-strategies). No study used digital filtering methods to determine V̇O~2max~.

```{r}
#| echo: false
#| label: tbl-strategies
#| tbl-cap: "Strategies for processing breath-by-breath data in the reviewed literature (n = 88)"

load("./data/bbb_strategies.Rda")

e_sort <- ext_count[order(ext_count$n, decreasing = TRUE), ]

knitr::kable(
  e_sort[, c("proc_combination", "perc")],
  col.names = c("Processing Strategy", "Usage"),
  align = "r",
  row.names = FALSE
)
```

@@

The calculation intervals for time-based averages of mixing chamber and breath-by-breath devices ranged from 5 to 60 seconds (see @fig-duration). 30-second intervals were most common to define V̇O~2max~, while some authors also often employed shorter (10-20 s) and longer (60 s) periods.

```{r}
#| echo: false
#| fig-cap: "Total durations of the calculation interval of V̇O~2max~ in the reviewed studies. ROBERT SCHLÄGT VOR HIER LIEBER EINE TABELLE ZU NEHMEN. ICH BIN FÜR DIE GRAFIK. WAS MEINST DU?."
#| label: fig-duration
#| out-width: '90%'

@@

```{r}
#| echo: false
#| fig-cap: "V̇O~2max~ varies by data processing strategy. Values are expressed relative to the V̇O~2max~ from a 30-second binned average — the most common strategy as determined by the review. Solid lines display the median, the shaded areas mark the interval between 10th and 90th percentile. Using moving average leads to systematically higher V̇O~2max~ values compared to binned time averages. Changing the averaging interval (in seconds or breaths) can lead to median changes in V̇O~2max~ as large as 5%. XLABEL GEÄNDERT IN 'DURATION' STATT 'PARAMETER'. OKAY?"
#| fig-scap: "Comparison of different data processing strategies."
#| label: fig-comparison
#| out-width: '90%'

knitr::include_graphics("./plots/comparison_xlabel.png")
```

@@

Despite calls to use moving averages or digital filters [@robergs2003; @robergs2010], binned time averages remain the most common data processing strategy to determine V̇O~2max~ in the reviewed literature (see @tbl-strategies). The present findings are generally in agreement with the findings of the non-systematic search by Midgley et al. @midgley2007 and the survey by Robergs et al. @robergs2010. It is somewhat surprising, that practices have not changed in recent years despite the publication of recommendations discouraging researchers from using binned averages [@robergs2010]. Using binned time averages leads to systematically lower V̇O~2max~ values as compared to moving averages (see @fig-comparison). The peak in oxygen uptake may be attained between two averaging intervals, resulting in an underestimation of V̇O~2max~. Binned time averages undermine the most important argument in favor of measuring breath-by-breath: the high temporal resolution of data. Despite these arguments speaking against the use of binned time averages, the present review demonstrates that they remain extremely common in the scientific literature.

@@

The different data processing strategies found in the literature directly bias the V̇O~2max~ determination (see @fig-comparison), and as such influence the classification of individuals, the evaluation of training success, and the assessment of V̇O~2max~ attainment. In accordance with previous findings [@johnson1998; @astorino2009; @sell2021] longer calculation intervals lead to lower V̇O~2max~ values (see @fig-comparison). The analyzed data shows median differences up to 5-7% between processing strategies, which is in accordance with previous research [@martin-rincon2019]. Some studies reported even higher mean differences of up to 20% [@myers1990], but only when including raw breath-by-breath data in the comparison. The evaluation of unprocessed raw data for its maximum is highly erroneous and as such is not performed in research (see @fig-duration); so there is no reason to compare it to other strategies. While previous research was often conducted in sedentary or recreationally trained individuals, we now present evidence, that a similar effect of data processing strategies on V̇O~2max~ exists in trained athletes. Since training interventions in trained athletes typically show improvements in V̇O~2max~ in the range of 0-6% [@parmar2021; @midgley2007a], variation caused by differing data processing strategies can bias the evaluation of their success.

@@

The exact impact of data processing strategies on the V̇O~2max~ is highly individual. Most research did present only comparisons of mean values, with results in accordance with those found here [@martin-rincon2019]. At the individual level, data processing strategies may impact V̇O~2max~ values with varying magnitudes. For example, for 10% of the investigated athletes a binned time average of 5 seconds leads to a V̇O~2max~ \<3% higher than by a 30-second average, while for another 10% the V̇O~2max~ was \>6% higher (see @fig-comparison). Current values reported and equation derived compare strategies on a group level [@martin-rincon2019], which improves comparison of group results for meta-analyses or group classifications. However, at the individual level these equations can only be applied with a large margin of error. Changes in the impact of different data processing strategies on V̇O~2max~ range from 1-2% in some individuals to more than 10% in others. Hence when evaluating V̇O~2max~ data from different tests in a single individual obtained by using different processing methods, there is no way to accurately compare these values even when the processing strategies are reported. While the comparison of V̇O~2max~ from different processing strategies require their reporting for an sufficient analysis on a group level, on the individual level the raw data from each test is required.

@@

> *"We measured breath-by-breath data during the ramp tests with a ZAN 600 USB device (nSpire Health, Inc., Longmont, CO, United States of America). The raw data was analyzed without any previous filtering by using a low-pass forward-backward Butterworth filter (each filter: 3rd order, 0.04 Hz cut-off) implemented in the spiro package for R version 0.0.4 [@nolte2022]. This strategy produces similar results as that recommended by Robergs et al. @robergs2010, but does not include a time lag."*

### 2022-11-17 scripts/comparison.Rmd
Adjust to feedback by RR

p_comp <- ggplot(res_tidy, aes(x = parameter, y = perdiff, colour = type, fill = type)) +
  geom_hline(
    yintercept = 0,
    colour = "grey",
    alpha = 0.3
  ) +
  stat_summary(geom = "line", fun = "median") +
  stat_summary(
    geom = "ribbon", 
    fun.data = "quant", 
    fun.args = list(lower = 0.1, upper = 0.9),
    alpha = 0.1, 
    colour = NA
  ) +
  scale_x_continuous(
    name = "Parameter",
    breaks = c(15, 30, 45, 60)
  ) +
  scale_y_continuous(
    name = "% to Reference",
    labels = scales::percent,
    limits = c(-0.053,0.1)
  ) +
  scale_color_manual(
    name = "Processing Strategy",
    values = met.brewer("Java", 3)
  ) +
  scale_fill_manual(
    name = "Processing Strategy",
    values = met.brewer("Java", 3)
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.8,0.8)
  )

@@

knitr::include_graphics("../plots/comparison.png")
```

>>>>

p_comp_pre <- ggplot(res_tidy, aes(x = parameter, y = perdiff, colour = type, fill = type)) +
  geom_hline(
    yintercept = 0,
    colour = "grey",
    alpha = 0.3
  ) +
  stat_summary(geom = "line", fun = "median") +
  stat_summary(
    geom = "ribbon", 
    fun.data = "quant", 
    fun.args = list(lower = 0.1, upper = 0.9),
    alpha = 0.1, 
    colour = NA
  ) +
  scale_y_continuous(
    name = "% to Reference",
    labels = scales::percent,
    limits = c(-0.053,0.1)
  ) +
  scale_color_manual(
    name = "Processing Strategy",
    values = met.brewer("Java", 3)
  ) +
  scale_fill_manual(
    name = "Processing Strategy",
    values = met.brewer("Java", 3)
  )

p_comp <- p_comp_pre +
  scale_x_continuous(
    name = "Parameter",
    breaks = c(15, 30, 45, 60)
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.8,0.8)
  )

@@

knitr::include_graphics("../plots/comparison.png")

# create plot with 'Duration' as x label
p_comp_duration <- p_comp_pre +
  scale_x_continuous(
    name = "Duration",
    breaks = c(15, 30, 45, 60)
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.8,0.8)
  )
# ggsave("../plots/comparison_xlabel.png", plot = p_comp_duration, width = 6, height = 4, dpi = 600, bg = "white")
```

### 2022-11-17 scripts/review.Rmd
Adjust to feedback by RR

percs <- scales::percent(ext_count$n / sum(ext_count$n))
ext_count$label <- paste0(ext_count$proc_combination, " (", percs, ")")
ext_count$subgroup <- c(1, 1, 2, 3, 4)

>>>>

percs <- scales::percent(ext_count$n / sum(ext_count$n))
ext_count$perc <- percs
ext_count$label <- paste0(ext_count$proc_combination, " (", percs, ")")
ext_count$subgroup <- c(1, 1, 2, 3, 4)

# save(ext_count, file = "../data/bbb_strategies.Rda")
